Draft_Application_Stochastic_Volatility

### 2021-07-19 Real Dataset SV.Rmd
Corrette tabelle rmd, risolto problema del seed per sequenza di particle filters

```{r include=FALSE}
Errorcomp1<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp1)<-c("N","BPF", "GPFOPT", "APF", "BAPF","SIS")
rownames(Errorcomp1)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp1[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp1[,2]<-c(0.4007204,0.15268841,0.08482937,0.04275829,0.02931792,0.2688306,0.09413161,0.04579035,0.02021174,0.01369827)
Errorcomp1[,3]<-c(0.4123198,0.15152308,0.06776933,0.06018919,0.03052592,0.2757273,0.09076196,0.03282099,0.02622987,0.01399114)
Errorcomp1[,4]<-c(0.5002458,0.2493751,0.122905,0.06863069,0.04399511,0.3905036,0.1812517,0.08131335,0.03401982,0.02529053)
Errorcomp1[,5]<-c(0.4687276,0.2698023,0.12737504,0.08064348,0.0513611,0.3711974,0.1945553,0.07408736,0.03614264,0.02515361)
Errorcomp1[,6]<-c(0.9168639,1.1055065,0.6250516,0.6200359,0.5118927,0.7275327,0.9179852,0.4971839,0.4475265,0.406363)

@@

```{r include=FALSE}
Errorcomp2<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp2)<-c("N","BPF", "GPFOPT", "APF", "BAPF", "SIS")
rownames(Errorcomp2)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp2[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp2[,2]<-c(0.3780316,0.13740936,0.06682471,0.02801391,0.04292242,0.2581917,0.08692049,0.03859926,0.01508258,0.01831794)
Errorcomp2[,3]<-c(0.3888922,0.13385416,0.05924883,0.05669256,0.04300498,0.2655844,0.08092348,0.03055189,0.02719531,0.02021422)
Errorcomp2[,4]<-c(0.4952102,0.228981,0.10257034,0.04911414,0.0280415,0.3869999,0.1717977,0.07240061,0.02690089,0.01949516)
Errorcomp2[,5]<-c(0.4601913,0.2447648,0.10985867,0.06133971,0.03314042,0.3651146,0.1838898,0.06507043,0.02966254,0.01913677)
Errorcomp2[,6]<-c(0.9103835,1.101557,0.6150409,0.6117618,0.5054665,0.7211173,0.914675,0.4895908,0.4419522,0.4022079)

>>>>

```{r include=FALSE}
Errorcomp1<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp1)<-c("N","BPF", "GPFOPT", "APF", "BAPF","SIS")
rownames(Errorcomp1)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp1[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp1[,2]<-c(0.4233094,0.15689352,0.06901099,0.03817009,0.03045272,0.2807802,0.09658088,0.03312132,0.01889245,0.01455814)
Errorcomp1[,3]<-c(0.3685259,0.15094281,0.07669050,0.03568058,0.02709059,0.2796141,0.09623692,0.03696833,0.01664805,0.01422964)
Errorcomp1[,4]<-c(0.5478362,0.2404408,0.08878446,0.05742351,0.04295610,0.4310335,0.1756985,0.05538968,0.03186140,0.02448565)
Errorcomp1[,5]<-c(0.5595929,0.2348842,0.10295053,0.06109947,0.05151115,0.4377886,0.1839363,0.06726034,0.03448388,0.02726281)
Errorcomp1[,6]<-c(0.9168639,1.1055065,0.6250516,0.6200359,0.5118927,0.7275327,0.9179852,0.4971839,0.4475265,0.406363)

@@

```{r include=FALSE}
Errorcomp2<-matrix(NA,ncol=6,nrow=10)
colnames(Errorcomp2)<-c("N","BPF", "GPFOPT", "APF", "BAPF", "SIS")
rownames(Errorcomp2)<-c("RMSE","RMSE","RMSE","RMSE","RMSE","MAE","MAE","MAE","MAE","MAE")
Errorcomp2[,1]<-c(10,100,1000,5000,10000,10,100,1000,5000,10000)
Errorcomp2[,2]<-c(0.4054868,0.13510456,0.04145471,0.02847469,0.03048093,0.2726597,0.08539766,0.02328878,0.01755582,0.01417144)
Errorcomp2[,3]<-c(0.3495018,0.14208597,0.06873795,0.04921716,0.03336987,0.2694089,0.09033775,0.03531985,0.02409677,0.01717600)
Errorcomp2[,4]<-c(0.5323702,0.2224267,0.07796291,0.03931358,0.02647522,0.4215135,0.1669123,0.05105029,0.02662432,0.01973858)
Errorcomp2[,5]<-c(0.5459719,0.2239766,0.07692431,0.05229897,0.02410626,0.4290946,0.1748428,0.05753199,0.03275473,0.01741627)
Errorcomp2[,6]<-c(0.9103835,1.101557,0.6150409,0.6117618,0.5054665,0.7211173,0.914675,0.4895908,0.4419522,0.4022079)
